|

### 2015-12-08 manuscript/manuscript_wtc3.Rmd
fixed chapter and title

---
title: "Chapter 3 Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

>>>>

---
title: |
  | Chapter 3 
  | Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---
